%!TEX TS-program = xelatex
\documentclass[a4paper, extended]{comcv}

\usepackage[english]{babel}

\title{Avinal's CV}
\fullname{Sumit}{Dhiman}{}
\cvtitle{Student, Programmer, Video Editor, Linux Enthusiast}
\website{https://sumitdhiman.live}{sumitdhiman.live}
\email{20bce091@nith.ac.in}
\github{https://github.com/lucifer1708}{GitHub}
\linkedin{https://www.linkedin.com/in/sumit-dhiman-20bce091}{LinkedIn}
\currentdate{Jan 2021}

\begin{document}
\section{Experience}
\combosection{Indian Society for Technical Education}{Coordinator | \href{https://istenith.com}{Website}}{Dec 2020-Present}{
  \begin{tightlist}
    \item Conducted many events and webinars as a part of NITH's technical society with over 100+ students.
    \item Hosted a workshop on Linux/Git and Github for over 150+ students.
    \item Deployed and Contributed in the production of many websites which include Backend and Frontend.
  \end{tightlist}
}

\combosection{C-Helix}{Coordinator | \href{https://chelix.festnimbus.com}{Website}}{Jan 2021-Present}{
  \begin{tightlist}
    \item Being part of team I handled many technical works like website creation.
    \item Conducted many events with over 100+ students.
  \end{tightlist}
}

\section{Projects}
\combosection{\href{https://github.com/lucifer1708/golang-REST-API-backend}{REST API - Crud App}}{Go Lang, Gin, Git, Gorm, SQLite}{}{
  \begin{tightlist}
    \item Includes the Login, User Registration, Get All Users, Authenticated Users, User by ID, etc
    \item Generates Restful API for login-signup and Authentication validation using JWT.
    \item Made in Go Lang to increase the Speed and reduce the resource usage of backend.
  \end{tightlist}

}

\combosection{\href{https://github.com/lucifer1708/cryptic-hunt}{Abhedya - The Cryptic Hunt}}{Python, Django, Docker, SQL, Celery, Shell Scripting}{}{
  \begin{tightlist}
    \item Includes features like Login-Signup, Password reset, Email verification, Dashboard, leaderboard, Hunt riddles page.
    \item Frontend made in Jinja templates using Django's builtin features
    \item Over 500+ registered using this website and 300+ people were playing at a time.
  \end{tightlist}
}

\combosection{\href{https://archfire.sourceforge.net}{ArchFire- The Archline Based Distro}}{Python, Cmake, C++, Linux, Shell Scripting}{}{
  \begin{tightlist}
    \item  Archlinux based distro with preconfigures DE/WMs.
    \item Packaged with calamares installer to make installation easy and hassel-free.
    \item With more than 22 downloads spanning countries like \textbf{Germany, Sweden, India,} etc.
  \end{tightlist}
}

\vspace{\topsep}
\combosection{Miscellanous Tools}{\href{https://github.com/lucifer1708}{GitHub}}{}{
  \begin{tightlist}
  \item \textbf{Push tool} use to upload any file over the null pointer server 0x0.st. \href{https://gist.github.com/lucifer1708/196a83a11efa5b1b17fd23a79dfb812e}{Link}
  \item \textbf{Golang CLI Tool} used to download wallpapers using argument and options \\ related to any keywords and number of pages respectively.\href{https://github.com/lucifer1708/go-practice-apps}{Link}
  \end{tightlist}
  }

\vspace{\topsep}
\section{Skills}
\combosection{Programming}{}{}{
  \begin{tightlist}
    \item Python, Go Lang, SQL, HTML, CSS, JavaScript 
    \item Docker, Yaml, Lua, Shell Scripting, Ansible
  \end{tightlist}
}
\combosection{Frameworks/Technologies}{}{}{
  \begin{tightlist}
    \item Django, Gorm, Gin, Echo, Flask, REST API 
    \item Kubernetes, Postgressql, , Shell Scripting, Ansible
    \item Git, Github, Github Actions, Celery
  \end{tightlist}
}
\combosection{Tools/Others}{}{}{
  \begin{tightlist}
    \item Scripting(Bash, Python, Go Lang), CI/CD, Linux/Unix, Windows 
    \item \LaTeX, Vim, Postman, Word, PowerPoint, Excel, Pandoc
  \end{tightlist}
}

\section{Education}
\combosection{National Institute of Technology, Hamirpur}{B.Tech in Civil Engineering}{2020-Present}{CGPA till 5\textsuperscript{th} semester - 7.57 

  \ifextended
    Courses -  Computer Networks, Operating Systems
  \else
  \fi
  }

\vspace{\topsep}
\combosection{Govt. Sr. Sec. School JolSapper}{Intermediate}{April 2019-March 2020}{Grade - 88.45\%}

% \vspace{\topsep}
% \section{Certifications}
% \combosection{Google IT Support Professional}{Coursera}{2020}{Computer Network, System Administration, Operating System, Cyber Security}
% \vspace{\topsep}
% \section{Others}
% \combosection{Computer Science Engineers' Society}{Coordinator}{2019-Present}{
%   Departmental Society of CSE NITH. Organizes Monthly Competitive Programming Contest and Bootcamp.
% }

\end{document}
